---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# The potential smoke-free dividend from quitting for smokers across local areas in England: A cross-sectional analysis - code repository

  
<!-- badges: start -->
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
<!-- badges: end -->

```{r}
#| label: load-packages
#| include: false

source("R/003 - load packages.R")

```

## Reproducibility 

Note that this repository uses the `renv` R package to produce a reproducible environment for this analysis. see [the package website](https://rstudio.github.io/renv/articles/renv.html) for more information.

## Citation
Please cite as:


## Computational environment

This repository was last updated on `r Sys.time()` and used the following computational environment and dependencies:

```{r}
#| cache: false

# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

The current Git commit details are (currently a private repository):

```{r, eval = FALSE}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```



